Reproducible Summary Tables with gtsummary

### 2020-12-10 RJtemplate_gtsummary_submission.tex
Updates from Overleaf

% code for tbl_summary() with arguments
\input{tbl_tbl_summary_family.tex}
\begin{example}
trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(by = trt, missing = "no") %>%
  add_p(test = all_continuous() ~ "t.test",
        pvalue_fun = ~style_pvalue(., digits = 2)) %>%
  add_n()
\end{example}
\begin{figure}[h!]
  \includegraphics[height=5cm]{summary_plus_plus.png}
  \centering
\end{figure}

@@

@@

@@

@@

@@

\hypertarget{tbl_uvregression}{%
\subsection{\texorpdfstring{\texttt{tbl\_uvregression()}}{tbl\_uvregression()}}\label{tbl_uvregression}}

>>>>

% code for tbl_summary() with arguments
\input{tbl_tbl_summary_family.tex}
\begin{example}
trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(by = trt, missing = "no") %>%
  add_n() %>%
  add_p(test = all_continuous() ~ "t.test",
        pvalue_fun = ~style_pvalue(., digits = 2))

\end{example}
\begin{figure}[h!]
  \includegraphics[height=5cm]{summary_plus_plus.png}
  \centering
\end{figure}

@@

\begin{example}
# create weighted survey object, keep only two counties
data(api, package = "survey")
svy_api <- 
  survey::svydesign(id = ~dnum, weights = ~pw, data = apiclus1, fpc = ~fpc) %>%
  subset(cname %in% c("Alameda", "Los Angeles"))

# summarize data
svy_api %>%
  tbl_svysummary(by = cname, 
                 include = c(growth, target, cname),
                 label = list(growth ~ "Growth",
                              target ~ "Target")) %>%
  add_p()
\end{example}
\begin{figure}[h!]
  \includegraphics[height=4cm]{svysummary.png}
  \centering
\end{figure}

@@

\begin{example}
trial %>%
  tbl_cross(row = stage, col = trt, percent = "cell") %>%
  add_p(source_note = TRUE)
\end{example}
\begin{figure}[h!]
  \includegraphics[height=4cm]{cross.png}
  \centering
\end{figure}

@@

\begin{example}
library(survival)

survfit(Surv(ttdeath, death) ~ trt, trial) %>%
  tbl_survfit(times = c(12, 24),
              label_header = "**{time} Month**") %>%
  add_p()
\end{example}
\begin{figure}[h!]
  \includegraphics[height=4cm]{survfit.png}
  \centering
\end{figure}

@@

% adding table describing fns for customization
\input{tbl_modify.tex}

@@

\begin{example}
glm(response ~ age + grade, trial, family = binomial) %>%
  tbl_regression(exponentiate = TRUE) %>%
  add_global_p()
\end{example}

\begin{figure}[h!]
  \includegraphics[height=4cm]{regression.png}
  \centering
\end{figure}

\subsection{\texorpdfstring{\texttt{tbl\_uvregression()}}{tbl\_uvregression()}}
\begin{example}
trial %>%
  select(response, age, grade) %>%
  tbl_uvregression(
    y = response, 
    method = glm,
    method.args = list(family = binomial),
    exponentiate = TRUE,
    pvalue_fun = ~style_pvalue(., digits = 2)
  ) %>%
  add_nevent() %>%
  add_global_p()
\end{example}

\begin{figure}[h!]
  \includegraphics[height=4cm]{uvregression.png}
  \centering
\end{figure}
